---
title: "RMarkDownTest"
author: "nJoooy"
date: "12 April 2019"
output:
  html_document:
    code_folding: hide
    number_sections: yes
    toc: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(eval = TRUE)
knitr::opts_chunk$set(results = TRUE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(fig.align = "center")
```

#Setup
##Here's the library you'll need for this TP


```{r set}
library(ggplot2)
library(dplyr)
library(gapminder)
```

#Analysis
##Here's the head of our dataset 


```{r gapminder, echo=FALSE}
head(gapminder)
```



##We can see, there are 6 features : country, continent, year, life expectation, population and gdp per capital.

##Now, let's see the size of our dataset : 



```{r pressure, echo=FALSE}
  nrow(gapminder)
```

##Let's the number of different years in the dataset

```{r year, echo=FALSE}
gapminder %>%
  select(year) %>%
  unique() %>%
  nrow()
```


##The number of country available per year ?

```{r country, echo=FALSE}
gapminder %>%
  group_by(year) %>%
  summarize( n=n() )
```

#Plot
##Here's the plot of the gdpPercap with the lifeExp

```{r plot, echo=FALSE}
gapminder %>%
  filter(year=="1952") %>%
  ggplot( aes(x=lifeExp, y=gdpPercap)) +
  geom_point()
```

#Improvements
##Try to determine which one is the outliers above

```{r outliers}
gapminder %>%
  filter(year=="1952", gdpPercap >= 60000) %>%
  group_by(country)
```

##It's Koweit in 1952, we erase him to have a better dataset

```{r erase}
gapminder %>%
  filter(year=="1952", country!="Kuwait") %>%
  ggplot( aes(x=lifeExp, y=gdpPercap))  +
  geom_point()
```

##With color it's always better

```{r color}
gapminder %>%
  filter(year=="1952", country!="Kuwait") %>%
  ggplot( aes(x=lifeExp, y=gdpPercap, color=continent))  +
  geom_point()
```


##With the appropriate size it's better

```{r size}
gapminder %>%
  filter(year=="1952", country!="Kuwait") %>%
  ggplot( aes(x=lifeExp, y=gdpPercap, color=continent, size=pop))  +
  geom_point()
```



##Interactive data 
```{r data, eval=TRUE}
library(DT)

datatable(gapminder, rownames = FALSE, filter="top", options = list(pageLength = 5, scrollX=T) )
```

```{r test}
library(devtools)
install_github("holtzy/epuRate")
library(epuRate)
```